{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-14 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updated fixes

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    The lemma theorem states targets
    \hyperref[prop:derive_ag_prox_grad_tript]
    {definition \ref*{prop:derive_ag_prox_grad_tript}}.

    \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]

@@

        Continue from 
        \hyperref[prop:derive_ag_prox_grad_tript]
        {definition \ref*{prop:derive_ag_prox_grad_tript}},
        we derive the non-smooth analogous case of the Lyapunov upper bound for all $t \in \mathbb N \cup \{0\}$: 

@@

@@

@@

@@

@@

        Define 

@@

            \phi_t(u) &:= 
            \tilde \eta_{t + 1} 
                f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
                % + 
                % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
            \right)\\
            \tilde \eta_{t + 1} \left(
                f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
                % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
                % + 
                g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
            \right). 

@@

        Then the update in the Generic Tri-Point algorithm 
        (\hyperref[def:ag_prox_grad_ppm]
            {definition \ref*{def:ag_prox_grad_ppm}}) 
        has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ if we ignore the difference between the constant terms $h(y_t^+)$, $f(y_t) + g(y_t)$ from above. 
        Therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
            {theorem \ref*{thm:ppm_descent_ineq}})
        which gives for all $x_*$: 

@@

            & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
            \frac{1}{2}\Vert x_t - x_*\Vert^2
            \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 

@@

            & \text{where }
            \phi_t(x_{t + 1}) =
            & \quad 
            \tilde \eta_{t + 1}
                f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
                % \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
                % + 
                g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
            \right). 

@@

        to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
            \begin{aligned}
                f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
                f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
                &\ge 
                f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
                \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
                f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
                + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
            \end{aligned}
            \tag{$[*]$}
        further consider
            \begin{aligned}
                g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
                &= g(y_t) + 
                \langle \partial g(y_t^+), 
                x_{t + 1} - y_t^+ + y_t^+ - y_t
                &= g(y_t) 
                + \langle \partial g (y_t^+),
                    x_{t + 1} - y_t^+
                    \partial g(y_t^+), y_t^+ - y_t
                g \text{ convex }\implies 
                &\ge 
                g(y_t^+) + 
                \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
            \end{aligned}
            \tag{$[\star]$}
        In the $([\star])$ derivation, we used the convexity of $g$ where 
            \langle \partial g(y_t^+), y_t - y_t^+\rangle
            &\le g(y_t) - g(y_t^+)
            \langle \partial g (y_t^+), y_t^+ - y_t \rangle
            g(y_t^+) - g(y_t). 
        Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality 
                \phi_t(x_{t + 1})
                &\ge 
                \tilde\eta_{t + 1}
                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
                    \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
                    g(y_t^+) + 
                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
                \tilde\eta_{t + 1}
                    h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
                    \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
                \right).
        Apply
        \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
        we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
            \phi_t(x_{t + 1}) &\ge 
            \tilde\eta_{t + 1} 
                h(z_{t + 1}) - 
                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
            \right). 
        Finally, from (\hyperref[lemma:grad_map_linearization]
            {lemma \ref*{lemma:grad_map_linearization}})
        we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
        With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
            & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
            \frac{1}{2}\Vert x_t - x_*\Vert^2
            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
            \tilde \eta_{t + 1}
                h(z_{t + 1}) - 
                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
            \right) - \tilde \eta_{t + 1} h(x_*)
            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
            \frac{1}{2}\Vert x_t - x_*\Vert^2
            & \quad \le
            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
            \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
            + \frac{1}{2}\left(
            \right) =: \Upsilon_{1, t + 1}^\text{AG}
            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
            \tilde\eta_{t + 1}
            \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
            \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
        It established the first inequality that we wish to prove. 
        Next, the smoothness of $f$ establish inequality: 
            \begin{aligned}
                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
                \langle \nabla f(y_t), y_t - z_t\rangle
                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
            \end{aligned}
            \tag{$[**]$}
        The convexity of $h$ establish 
            \begin{aligned}
                g(z_{t + 1}) + 
                \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
                &\le g(z_t)
                g(z_{t + 1}) - g(z_t)
                    \partial g (z_{t +1}), 
                    z_{t + 1} - z_t
                \rangle. 
            \end{aligned}
            \tag{$[\star *]$}    
        Adding $([**]), ([\star *])$ yields 
            \begin{aligned}
                \Upsilon_{2, t + 1}^{\text{AG}} := 
                    \nabla f(y_t) + \partial g(z_{t+1}), 
                    z_{t + 1} - z_t
                \frac{L}{2}
                    z_{t + 1} - y_t
                \Vert^2. 
            \end{aligned}
        Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
            {lemma \ref*{lemma:grad_map_lemma_first}}), 
        $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 

    \begin{theorem}[Generic AG Convergence]
    \label{thm:generic_ag_convergence}
        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
        \begin{align*}
            \Phi_t &= \left(
                \sum_{i = 1}^{t} \tilde\eta_{i}
            \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
            \\
            \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
        \end{align*}
        if there is a choice of $\eta_i, \tilde \eta_i$ in 
        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}} such that we have 
        \begin{align*}
            & \Phi_{t + 1} - \Phi_{t}\left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right) =
            \Upsilon_{2, t + 1}^{\text{AG}} + 
            \Upsilon_{1, t + 1}^{\text{AG}} 
            \le \delta_{t + 1} \quad 
            \forall t \in \mathbb N, 
            \\
            & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
        \end{align*}
        Then with
        \begin{align*}
            S_t &:= \sum_{i = 1}^{t} \delta_i
            \\
            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
        \end{align*}
        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$. 
    \end{theorem}
    \begin{proof}
        By definition we have
        {\footnotesize
        \begin{align*}
            \Phi_{t + 1} - \Phi_t 
            &= 
            \left(
                \sum_{i = 1}^{t+1} \tilde\eta_{i}
            \right) (f(z_{t + 1}) - f(x_*)) 
            - 
            \left(
                \sum_{i = 1}^{t} \tilde\eta_{i}
            \right) (f(z_{t}) - f(x_*)) 
            + \frac{1}{2}\Vert x_t - x_*\Vert^2
            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
            \\
            &= 
            \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
            +
            \left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right)(f(z_{t + 1}) - f(z_t))
            + \frac{1}{2}\Vert x_t - x_*\Vert^2
            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
            \\
            &= \left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
        \end{align*}
        }
        Telescoping we have 
        \begin{align*}
            \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
            \\
            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
            \\
            \Phi_T - \Phi_0 &\le 
            \sum_{i = 1}^{T}\delta_i = S_{T}. 
        \end{align*}
        So then $\Phi_T - \Phi_0$ yields: 
        $$
        \begin{aligned}
            \sigma_T (f(z_t) - f(x_*)) 
            + \frac{1}{2}\Vert x_t - x_*\Vert^2 
            - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
            &\le S_{T}
            \\
            \implies 
            \sigma_T(f(z_t) - f(x_*))
            &\le 
            S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
            \\
            f(z_t) - f(x_*) &\le 
            \sigma_T^{-1}\left(
                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
            \right),
        \end{aligned}
        $$
        which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
        When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
    \end{proof}

    \begin{theorem}[Constraints on the PPM stepsize sequence]
        \label{thm:ag_generic_stepsize_constrants}
        \;\\
        Algorithm formulated in 
        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
        converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
        \begin{align*}
            \begin{cases}
                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
                = 
                \epsilon_{t + 1} \tilde \eta_{t + 1}
                & \forall t \in \mathbb N, 
                \\
                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
                & \forall t \in \mathbb N. 
            \end{cases}
        \end{align*}
        Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made to characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
        Then the convergence rate can be formulated by
        \begin{align*}
            \Phi_{t + 1} - \Phi_t =
            \Upsilon_{1, t + 1}^\text{AG} + 
            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
        \end{align*}
        When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
        \begin{align*}
            \begin{cases}
                a_{t + 1} = (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
                \right), 
                \\
                c_{t + 1} = a_t^2.     
            \end{cases}
        \end{align*}
        As a consequence: 
        \begin{enumerate}
            \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
            \item it simplifies the algorithm to FISTA. 
            \item and $a_t$ is the famous Nesterov momentum sequence. 
        \end{enumerate}

>>>>

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    The following lemma establish an upper bound for quantities used in the Lypunov functions for the convergence rate of 
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}
    \begin{lemma}[Lyapunov Inequality]

@@

        Let $h = f + g$ be a sum of $f$ that is $L$-Lipschitz smooth convex, and $g$ be convex.
        Fix any $\bar x, x, \tilde\eta > 0$, define

@@

            \phi(u) &:= \tilde\eta
                h( \mathcal T_L\bar x) + \langle \mathcal G_L\bar x, u - \bar x\rangle
                + \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2 
            x^+ &:= 
            \prox{\phi}(x) = x - \tilde \eta\mathcal G_L \bar x. 
        with $x_*$ being the minimizer of $h$, it has 
            \Upsilon_{1}  &:= 
            \tilde \eta(h(\mathcal T_L \bar x) - h(x_*))
            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2)
            \tilde \eta 
            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            \frac{1}{2}\Vert x^+ - x\Vert^2, 
            \forall z':
            \Upsilon_2 &:= 
            h(\mathcal T_L \bar x) - h(z') 
            \langle \mathcal G_L\bar x, \mathcal T_L \bar x - z'\rangle + 
            \frac{L}{2}\Vert \mathcal T_L \bar x - \bar x\Vert^2. 
    \begin{observation}
        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, anchored at $\bar x$ by 
        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
    \end{observation}
        Directly observe that we have 
            \quad &
            h(\mathcal T_L\bar x) + 
            \langle \mathcal G_L \bar x, u - \bar x\rangle + 
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2

@@

            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
            \langle \mathcal G_L \bar x, \mathcal T_L \bar x - \bar x\rangle
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x \Vert^2
            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
                L (\bar x - \mathcal T_L \bar x)
                , 
                \mathcal T_L \bar x - \bar x
            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
            h(\mathcal T_L \bar x) + 
            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
            - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2. 
        By PPM descent inequality
        \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}
        , let $x_*$ be a minimizer, it claims that 
            & 
            \phi(x^+) - \phi (x^*) + 
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2
            - \frac{1}{2}\Vert x^+ - x\Vert^2
            \tilde 
            \eta 
                h(\mathcal T_L \bar x) + 
                \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
                - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            - \tilde \eta h (x_*)
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2

@@

            - \frac{1}{2}\Vert x^+ - x\Vert^2
            \tilde \eta (h(\mathcal T_L\bar x) - h(x_*))  
                \Vert x^+ - x_*\Vert^2 - 
                \Vert x - x_*\Vert^2
            & \le 
            \tilde \eta 
            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
            \frac{1}{2}\Vert x^+ - x\Vert^2. 
        Next, for all $z, z'$, it would have by smoothness of $f$: 
            f(z) - f(z') &= 
            f(z) - f(\bar x) + f(\bar x) - f(z')
                \nabla f(\bar x), z - \bar x
            \frac{L}{2}\Vert z - \bar x\Vert^2 
                \nabla f(\bar x), 
                \bar x - z'

@@

            \langle \nabla f(\bar x), z - z'\rangle
            \frac{L}{2}\Vert z - \bar x\Vert^2. 
        The convexity of $g$ yields: 
            g(z) + 
                \partial g(z), z' - z
            &\le g(z')
            g(z) - g(z') 
            \langle \partial g(z), z - z'\rangle. 
        Adding them yield 
            h(z) - h(z') &\le 
            \langle \nabla f(\bar x) + \partial g(z), z - z'\rangle + 
            \frac{L}{2}\Vert z - \bar x\Vert^2. 
        Setting $z = \mathcal T_L \bar x$, we have the desired results. 
        This lemma is designed to work with 
        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}.
        Set $\bar x = y_t, x = x_t$, then 
            x^+ &= x_t - \mathcal G_L y_t = x_{t + 1},
            z_{t + 1} &= \mathcal T_L y_t = \mathcal T_L \bar x.
        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, 
        the results can be written as 
            &:= 
            \tilde \eta_{t + 1}(h(z_{t + 1}) - h(x_*))
            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2)
            \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
            \frac{\tilde \eta_{t + 1}L}{2}
                y_t - z_{t + 1}
            \Vert^2
            \frac{1}{2}
            \Vert x_{t + 1} - x_t\Vert^2,  
            &:= 
            h(z_{t + 1}) - h(z_t) \le 
            \langle \mathcal G_L \bar x, z_{t + 1} - z_t \rangle + 

@@

    \begin{theorem}[Generic AG Convergence]
    \label{thm:generic_ag_convergence}
        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
        \begin{align*}
            \Phi_t &= \left(
                \sum_{i = 1}^{t} \tilde\eta_{i}
            \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
            \\
            \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
        \end{align*}
        if there is a choice of $\eta_i, \tilde \eta_i$ in 
        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}} such that we have 
        \begin{align*}
            & \Phi_{t + 1} - \Phi_{t} =
            \left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right)\Upsilon_{2, t + 1}^{\text{AG}} + 
            \Upsilon_{1, t + 1}^{\text{AG}} 
            \le \delta_{t + 1} \quad 
            \forall t \in \mathbb N, 
            \\
            & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
        \end{align*}
        Then with
        \begin{align*}
            S_t := \sum_{i = 1}^{t} \delta_i,
            \quad 
            \sigma_t := \sum_{i = 1}^{t}\tilde \eta_i, 
        \end{align*}
        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T \le 0$. 
    \end{theorem}
    \begin{proof}
        By definition we have
        {\footnotesize
        \begin{align*}
            \Phi_{t + 1} - \Phi_t 
            &= 
            \left(
                \sum_{i = 1}^{t+1} \tilde\eta_{i}
            \right) (f(z_{t + 1}) - f(x_*)) 
            - 
            \left(
                \sum_{i = 1}^{t} \tilde\eta_{i}
            \right) (f(z_{t}) - f(x_*)) 
            + \frac{1}{2}\Vert x_t - x_*\Vert^2
            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
            \\
            &= 
            \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
            +
            \left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right)(f(z_{t + 1}) - f(z_t))
            + \frac{1}{2}\Vert x_t - x_*\Vert^2
            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
            \\
            &= \left(
                \sum_{i = 1}^{t} \tilde \eta_i
            \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
        \end{align*}
        }
        Telescoping we have 
        \begin{align*}
            \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
            \\
            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
            \\
            \Phi_T - \Phi_0 &\le 
            \sum_{i = 1}^{T}\delta_i = S_{T}. 
        \end{align*}
        So then $\Phi_T - \Phi_0$ yields: 
        $$
        \begin{aligned}
            \sigma_T (f(z_t) - f(x_*)) 
            + \frac{1}{2}\Vert x_t - x_*\Vert^2 
            - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
            &\le S_{T}
            \\
            \implies 
            \sigma_T(f(z_t) - f(x_*))
            &\le 
            S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
            \\
            f(z_t) - f(x_*) &\le 
            \sigma_T^{-1}\left(
                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
            \right),
        \end{aligned}
        $$
        which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
        When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
    \end{proof}

    \begin{theorem}[Constraints on the PPM stepsize sequence]
        \label{thm:ag_generic_stepsize_constrants}
        \;\\
        Algorithm formulated in 
        converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies

@@

                & \forall t \in \mathbb N, 
                & \forall t \in \mathbb N. 

@@

        Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made to characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
        Then the convergence rate can be formulated by

@@

            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
        When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 

@@

                c_{t + 1} = a_t^2.     

@@

        As a consequence: 
            \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
            \item it simplifies the algorithm to FISTA. 
            \item and $a_t$ is the famous Nesterov momentum sequence. 
